---
title: "loryR Quick and Easy"
author: "Kent Russell"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{loryR Quick and Easy}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

`loryR` offers the fine dependency-free slider [`lory.js`](https://github.com/meandmax/lory) from Maximilian Heinz as a `htmlwidget`.  R users can employ a slider (or embedded slideshow/gallery) like this in many ways.    Let's look at two different uses to help us explore how we might work with `loryR`.

### Quick Install

```{r eval = F}
devtools::install_github( "timelyportfolio/loryR" )
```

### Use 1 | RStudio Gallery

As we bang away in RStudio, we can unintentionally collect quite a few plots in our Plots tab.  I often want to quickly view or share some or all of these plots.  The function `rstudio_gallery()` in `loryR` solves this problem. 

```{r eval = F}
##### run these one at a time
#####   to make some fake sample plots
plot( 1:10 )
contour( volcano )
dotchart(VADeaths, main = "Death Rates in Virginia - 1940")
coplot(lat ~ long | depth, data = quakes)
sunflowerplot(iris[, 3:4])
```

Now let's create our `loryR` gallery of our wonderful creations.

```{r eval = F}
library(loryR)

loryR(
  rstudio_gallery()
  , images_per_page = 2
  , options = list( rewind = TRUE )
  , height = 500
  , width = 500
)
```


*I wish I was able to get the actual slider to appear right here, but I haven't found out yet how to when knitting a vignette.*  Please try it though on your machine.  I think you will like the result.

### Use 2 | In a Vignette

Often in a package documentation context, a nice summary view might entice the reader to more thoroughly explore your package.  Let's pretend we our making a vignette for the really neat package [`tmap`](http://cran.r-project.org/web/packages/tmap/index.html) from Martijn Tennekes.  Here is one way to make a nice summary slider with the tmaps to include at the top of the vignette.

```{r message = FALSE, warning = FALSE, error = FALSE}
library(tmap)
library(loryR)
library(pipeR)  ## feel free to use magrittr if you prefer

### all of the tmap examples are from the tmap vignette
###  https://github.com/mtennekes/tmap/blob/master/pkg/vignettes/tmap-nutshell.Rmd
data(Europe)

list(
  quote(qtm(Europe))
  ,quote({
    qtm(Europe, fill="gdp_cap_est", text="iso_a3", text.size="AREA",
        root=5, fill.title="GDP per capita", 
        fill.textNA="Non-European countries", theme="Europe")
  })
  ,quote({
    data(rivers)
    data(metro)
    
    tm_shape(Europe) +
        tm_fill("pop_est_dens", style="kmeans", textNA="Non-European countries"
                , title="Country population density (per km2)") +
        tm_borders() +
        tm_shape(rivers) +
        tm_lines("dodgerblue3") +
        tm_shape(metro) +
        tm_text("name", size="X2010", scale=1, ymod=-.02, root=4, size.lowerbound = .60, 
                bg.color="yellow", bg.alpha = .5) + 
        tm_bubbles("X2010", "red", border.col = "black", border.lwd=1
                   , size.lim = c(0, 11e6), sizes.legend = seq(2e6,10e6, by=2e6)
                   , title.size="City Population") +
    tm_shape(Europe) +
        tm_text("iso_a3", size="area", scale=1.5, root=8, size.lowerbound = .40, 
                fontface="bold", case=NA, fontcolor = "gray35") + 
    tm_layout_Europe("Map of Europe", legend.width=.6)
  })
  ,quote({
    tm_shape(Europe) +
      tm_fill("gdp_cap_est", style="kmeans", title="GDP per capita") +
      tm_facets("part") +
      tm_layout_Europe()
  })
  ,quote({
    data(World)

    rivers$constant <- factor("Rivers")
    tm_shape(World) +
        tm_fill() +
    tm_shape(rivers) +
        tm_lines(col="constant", palette="dodgerblue3", title.col="World map") +
        tm_layout_World()
  })
) %>>%
  lapply(
    function(plot_expr){
      tf <- tempfile()
      png(tf, width = 600, height = 500, units = "px")
        print(eval(plot_expr))
      dev.off()
      base64enc::dataURI(file=tf, mime="image/png")
    }
  ) %>>%
  loryR( images_per_page = 1, options = list(rewind=TRUE), height = 600, width = 650 )
```

### Thanks

Thanks so much

- [`lory.js`](https://github.com/meandmax/lory) from Maximilian Heinz
- Ramnath Vaidyanathan and RStudio for `htmlwidgets`
- all the contributors to `R` and `JavaScript`
